\papertitle

### 2012-10-13 manuscript.tex
Squashing passive voice, various grammar edits.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becominga well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in
~\cite{Shigeoka:ornithopter}. Design and control of the sub 15 gram DelFly
ornithopter is described by deCroon et al.~\cite{delfly:design}.
In contrast, there is little previous work on guidance of flapping wing 
MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub 20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

@@

Many of the methods for
controlling these platforms make extensive use of GPS in outdoor
environments and expansive
motion capture systems in indoor environments~\cite{kingston:timeattitude}\cite{kanade:3dvision}. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

Rather than power-intensive PC processors, we used the ARM-based 
BeagleBoard single-board computer as reference computation platform. The
BeagleBoard consumes approximately 1 watt while running our computer vision 
and control algorithms. It uses the same processor as popular sub-10 gram 
processor modules--such as the Gumstix Overo and LogicPD Torpedo--which are 
light enough for deployment on millirobotic ground vehicles. We pair the 
BeagleBoard with an off-the-shelf consumer USB web camera, for similar image 
quality and resolution to the miniature camera modules available at 
millirobot scale. The BeagleBoard communicates with the H$^2$Bird using a 
USB radio module which implements the IEEE 802.15.4 wireless standard.
%TODO footnotes: Gumstix, LogidPD

Our ground station software is based on the Ubuntu Linux\footnote{\raggedright Ubuntu: 
Canonical Ltd., \href{http://www.ubuntu.com/}{http://www.ubuntu.com/}} distribution
modified with a custom version of the Linux kernel. We use the Python
\footnote{\raggedright Python: Python Software Federation, \href{http://www.python.org/}
{http://www.python.org/}} programming language for control, robot communication, 
and telemetry, and the OpenCV\footnote{\raggedright OpenCV: Willow Garage, 
\href{http://opencv.willowgarage.com/wiki/}{http://opencv.willowgarage.com/wiki/}} 
computer vision libraries for image capture and processing.
%TODO footnotes: Ubuntu, Linux, Python, OpenCV
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}
%TODO ryan

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this work use a diagonal covariance matrix 
with variance 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

@@

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
Remote guidance of the H$^2$Bird is performed by commanding relative changes in the
reference orientation. With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. Incremental changes to the H$^2$Bird pitch and yaw are
then commanded according to a PID control law, with positive altitude error
corresponding to negative incremental pitches and positive horizontal error
corresponding to negative incremental yaw. The controller integrator term is windowed
to prevent windup when the bird is being launched, and the derivative term was tuned
by hand to dampen oscillations associated with the system latency [?].

@@

To model the yaw motion of the ornithopter, we developed a one-dimensional model using the physical heading angle as the output and the heading angle set by the ground station as the input. This model accounts for both the yaw dynamics of the ornithopter and the internal PID controller on the actuator inputs for the tail rotor. We decided upon a one-dimensional model to reduce the complexity of the overall model and enable simple angle inputs and outputs, which is similar to our methods during experimentation. The format of the model we decided up on is shown in Equation~\ref{eq:plain_model}.

@@

To model the translational position of the ornithopter, we used a form of Dubin's car model~\cite{lavalle:planning} with the angular position, $\theta$ as an input rather than a state. So the overall motion of the system can be modeled as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (\ref{eq:plain_model}) with the angular setpoint provided by the ground station as the input.

@@

The model of the ground station combines both the camera model and the
computational model for pose estimation. The camera model contains both a
latency, which would occur in between the "camera" and "ornithopter dynamics"
in Fig.~\ref{fig:block_diagram}, and a model for the viewing angle. The
viewing angle for the camera is modeled as a pixel map from one edge of a
63$^{\circ}$ viewing triangle to the other. The camera has an image width of
640 pixels. The desired heading angle in degrees for a given distance from the
camera is calculated according to Equation~\ref{eq:desired_heading}, where d
is the distance of the robot in front of the camera and x is the horizontal
position of the robot relative to the center of the window in meters. This
formula models the fact that the camera cannot determine the depth of the
robot.

@@

The computational model consists of the latency for the operations required to
run the particle filter and calculate the input to send to the robot.

@@

In total, 80 trials were run over a variety of starting positions. The goal of
our experiments was to verify the model described in
Secttion~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a grid
along the edges of the camera viewplane in 0.05 meter increments from the
window to determine the success rate on the edges of the testing space. We
conducted 20 additional trials directly in front of the camera to determine
the success rate near the center of the testing space. After every 5 trials,
we replaced the current battery with a fully charged one.

@@

The latency that we measured for the camera was 25ms and the measured
partiicle filter computational latency was 12.5ms.

@@

The results of our experimental trials are shown in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Fig.~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over- or under-compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
The power, size, and weight constraints of micro air vehicle (MAV) 
platforms significantly limit on-board sensing and computational 
resources, and thus the complexity of the control and state estimation 
algorithms which can be executed on-board. These constraints are 
particularly severe for flapping wing MAVs, a class of MAVs that have inherently superior 
safety, and noise profile to rotor craft MAVs, but at the 
expense of payload weight.
%Intro portion about previous works in ornithopter coorperative control/
%modeling ( won't necessarily stay in this spot)
Modeling and control of flapping wing MAVs is becoming a well studied subject\cite{floreano:flying}. 
Shigeoka discusses velocity and altitude control in ~\cite{Shigeoka:ornithopter}. 
Design and control of the sub--15 gram DelFly ornithopter is described by 
deCroon et al.~\cite{delfly:design}. In contrast, there is little previous work 
on guidance of flapping wing MAVs. Baek demonstrated altitude control with an external 
camera~\cite{baek:altitude}. de Croon et al. demonstrated obstacle avoidance 
with an onboard camera and offboard processing~\cite{delfly:avoid}. For sub--20 gram
ornithopters, Baek et al. \cite{baek:tracking} is one of the few examples of
completely autonomous target seeking.
%[However, these papers do not study the system blah blah blah.]

@@

Many of the methods for controlling these platforms make extensive use of GPS in outdoor
environments and expansive motion capture systems in indoor environments
~\cite{kingston:timeattitude}\cite{kanade:3dvision}. While operating indoors, using
GPS to estimate the pose of the MAV is not possible, and motion capture
requires expensive and stationary modification of the environment. The power
and payload limits on MAVs make on-board sensing difficult, so multi-agent
cooperative control schemes are apt solutions.

@@

Rather than power-intensive PC processors, we used the ARM-based 
BeagleBoard single-board computer as reference computation platform. The
BeagleBoard consumes approximately 1 watt while running our computer vision 
and control algorithms. It uses the same processor as popular sub--10 gram 
processor modules--such as the Gumstix Overo and LogicPD Torpedo--which are 
light enough for deployment on millirobotic ground vehicles. We pair the 
BeagleBoard with an off-the-shelf consumer USB web camera, for similar image 
quality and resolution to the miniature camera modules available at 
millirobot scale. The BeagleBoard communicates with the H$^2$Bird using a 
USB radio module which implements the IEEE 802.15.4 wireless standard.
%TODO footnotes: Gumstix, LogidPD

Our ground station software is based on the Ubuntu Linux\footnote{\raggedright Ubuntu: 
Canonical Ltd., \href{http://www.ubuntu.com/}{http://www.ubuntu.com/}} distribution
modified with a custom version of the Linux kernel. We use the Python
\footnote{\raggedright Python: Python Software Federation, \href{http://www.python.org/}
{http://www.python.org/}} programming language for control, robot communication, 
and telemetry, and the OpenCV\footnote{\raggedright OpenCV: Willow Garage, 
\href{http://opencv.willowgarage.com/wiki/}{http://opencv.willowgarage.com/wiki/}} 
computer vision libraries for image capture and processing.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Concept and Algorithms}
%TODO ryan

@@

%............................................................................%
\subsubsection{Motion Model}
Our motion model (Eq.~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. In Eq.~\ref{eq:motion_model}, 
$x^{[i]}_t$ is the state of the $i^\text{th}$ particle at time $t$, $\Sigma$ 
is a chosen covariance matrix, and $b$ is vector of the height and width of 
the camera frame.
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
The experiments presented in this work use a diagonal covariance matrix 
with a variance of 256, and an $\epsilon$ of 0.3. We find that the Gaussian 
transition model is sufficient for tracking motion in which frame-to-frame 
position changes are relatively small. The $\epsilon$-random uniform 
transitions increase tracking robustness, by forcing the filter to always 
sample all of the pixel space. This prevents overconfidence and collapse, 
and decreases reacquisition delay.

@@

%----------------------------------------------------------------------------%
\subsection{Cooperative Visual Servoing}
\label{sec:visual_servoing_concept}
Remote guidance of the H$^2$Bird is performed by commanding relative changes in the
reference orientation. With estimates of the vehicle pose, we calculate an altitude
error and horizontal error. The ground station then commands incremental changes to 
the H$^2$Bird pitch and yaw are according to a PID control law, with positive altitude error
corresponding to negative pitch increments and positive horizontal error
corresponding to negative yaw increments. We window the controller integrator term 
to prevent windup when the bird is being launched, and tuned the derivative term
to dampen oscillations associated with the system latency [?].

@@

To model the yaw motion of the ornithopter, we developed a one-dimensional model using the physical heading angle as the output and the heading angle set by the ground station as the input. This model accounts for both the yaw dynamics of the ornithopter and the internal PID controller on the actuator inputs for the tail rotor. We decided upon a one-dimensional model to reduce the complexity of the overall model and enable simple angle inputs and outputs, which is similar to our methods during experimentation. The model format is shown in Equation~\ref{eq:plain_model}.

@@

To model the translational position of the ornithopter, we used a form of Dubin's car model~\cite{lavalle:planning} with the angular position, $\theta$ as an input rather than a state. The overall motion of the system can be modeled as shown in Equation~\ref{eq:total_model_plain}, where $\theta$ is the time domain output of (\ref{eq:plain_model}) with the angular setpoint provided by the ground station as the input.

@@

The model of the ground station combines both the camera model and the
computational model for pose estimation. The camera model contains both a
latency, which would occur in between the "camera" and "ornithopter dynamics"
in Fig.~\ref{fig:block_diagram}, and a model for the viewing angle. We model the 
viewing angle for the camera as a pixel map from one edge of a
63$^{\circ}$ viewing triangle to the other. The camera has an image width of
640 pixels. The desired heading angle in degrees for a given distance from the
camera is calculated according to Equation~\ref{eq:desired_heading}, where $d$
is the distance of the robot in front of the camera and $x$ is the horizontal
position of the robot relative to the center of the window in meters. This
relation reflects the fact that the camera cannot determine the depth of the
robot.

@@

The computational model accounts for the latency added by the operations required to
run the particle filter and calculate the input to send to the robot.

@@

In total, we ran 80 trials over a variety of starting positions. The goal of
our experiments was to verify the model described in
Secttion~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a grid
along the edges of the camera viewplane in 0.05 meter increments from the
window to determine the success rate on the edges of the testing space. We
conducted 20 additional trials directly in front of the camera to determine
the success rate near the center of the testing space. After every 5 trials,
we replaced the current battery with a fully charged one.

@@

The latency that we measured for the camera was 25ms, and the measured
partiicle filter computational latency was 12.5ms.

@@

The results of our experimental trials are shown in
Figs.~\ref{fig:flight_paths} and~\ref{fig:flight_paths_feasible}. For
initial conditions in the middle of the testing space and in front of the
camera, we achieved a success rate of 80\%. This case is depicted in
Fig.~\ref{fig:flight_paths_feasible}. As we moved towards the edges of the
feasible region in Fig.~\ref{fig:flight_paths}, the success rate diminishes
to 50\% because of several factors. On the edges of the camera frame, the yaw
control inputs are large in magnitude, although this is not necessary in all
cases. Since the control algorithm we are using has no notion of depth, it
applies the same control input whether the ornithopter is close to the camera,
where small changes in heading are adequate, or far away from the camera,
where large changes in heading are necessary. Due to this phenomenon, the
controller often over or under--compensates in certain regions, depending upon
the PID tuning and the distance from the camera. Tracking noise can also cause
passage negotiation to fail. Variations in the H$^2$Bird hand launch can cause
the system to respond differently for similar initial conditions. In addition,
the H$^2$Bird battery was changed approximately every 5 tests, adding more
variation to the H$^2$Bird performance by affecting the motor power output.
